---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## count

<!-- badges: start -->
<!-- badges: end -->

count is a package created for STAT 545 assignment B2, making an R package. This package contains functions that can aid in data analysis and data organization.

#### Installation

You can install the development version of count from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/")
```

#### Functions
The only function currently in count is the count_all_missing_by_group function.

#### What the function?
count_all_missing_by_group is a function that counts missing values for all columns by group, providing a summary tibble of missing value (i.e. NAs) as output. This function is valuable for early assessments of data, spot-checking for missing values among levels and categories. 

#### Examples
I know you're eager, so here is the function in action:

Let’s count up all the missing values in the airquality dataset by the Month variable:
```{r}
count::count_all_missing_by_group(airquality, Month)
```

Cool. You can do the same thing but pipe |> (base R) or %>% (dplyr) it if that's more your speed.
```{r}
airquality |> 
  count::count_all_missing_by_group(Month) 
```

One more! The optional `.groups` argument allows us to keep the output grouped by the grouping column.

```{r}
count::count_all_missing_by_group(airquality, Month, .groups = "keep")
```

